Model Fitting

### 2018-09-11 contest/model-fitting/model-fitting.Rmd
please work

```{r}
ind_mod = brm(pointswon ~ ioc_fac + hand_fac + round + rank + opponent_rank + minutes + (1 + tournament |name_int), data = gs_players, family = gaussian())
```

@@

```{r}
plot(marginal_effects(basemod, effects = "tournament"))
plot(marginal_effects(country_mod, effects = "tournament"))
plot(marginal_effects(ind_mod, effects = "tournament"))
```

### Model Comparison (tennis knowledge)

Checks:
* Serena should be good on hard surface
* Nadal should be good on clay 
* Federer should be good on grass

@@

```

>>>>

```{r}
ind_mod = brm(pointswon ~ ioc_fac + hand_fac + round + rank + opponent_rank + minutes + (1 + tournament |name_int), data = gs_players, family = gaussian())
ind_lmer = lmer(pointswon ~ ioc_fac + hand_fac + round + rank + opponent_rank + minutes + (1 + tournament |name_int), data = gs_players)
```

@@

@@

save(basemod, country_mod, ind_mod, file = "stan-model-fits.RData")
plot(marginal_effects(basemod, effects = "tournament"))
plot(marginal_effects(country_mod, effects = "tournament"))
plot(marginal_effects(ind_mod, effects = "tournament"))
```
